Under-approximation of reachability through static analysis in multivalued asynchronous networks

### 2013-04-02 parts/sa.tex
add section 3.3: reachability of a state

\todo{La méthode permet aussi de conclure sur l'accessilibité d'un état (global ou partiel)}

>>>>

\subsection{Reachability of a state}

%\newcommand{\total}{{total}}
%\newcommand{\reach}{{reach}}
\newcommand{\total}{\tau}
\newcommand{\reach}{\sigma}

We note that the semantics of PH with $2$ priorities defined in \pref{ssec:hypothesis} allows to model cooperative sorts representing a coherent configuration of a set of sorts.
As the method presented in this section allows to efficiently conclude on the reachability of a process,
we can derive a new method to conclude about the reachability of a state of components.
Indeed, let $\PH = (\PHs, \PHl, (\PHh^{(1)}, \PHh^{(2)}))$ be a PH and suppose we want to study the reachability of a state $s \in \PHl$.
Let $\PH' = (\PHs', \PHl', (\PHh'^{(1)}, \PHh'^{(2)}))$,
with: $\PHs' = \PHs \cup \{ \total, \reach \}$, $\PHl' = \PHl \times \PHl_\total \times \PHl_\reach$,
where $\total$ is a cooperative sort an all components $\components$ of $\PH$, thus $\PHl_\total = \underset{a \in \components}{\times} \PHl_a$,
and $\reach$ is a component with $\PHl_\reach = \{ \reach_0, \reach_1 \}$.
We also define $\PHh'^{(1)}$ as the set $\PHh^{(1)}$ completed with all actions updating the cooperative sort $\total$,
and $\PHh'^{(2)} = \PHh^{(2)} \cup \{ \PHfrappe{\pfp_s(\total)}{\reach_0}{\reach_1} \}$;
therefore, the additional action in $\PHh'^{(2)}$ allows to conclude on the reachability of process $\pfp_s(\total)$, that is, on the reachability of $s$ (considering only the components).
